### 2021-09-08 input/proposal.tex
wip

\begin{proof}
  Figure~\ref{fig:proofB} depicts all possible cases that need
  appropriate purging. A chain of \processes $[a, b, c, d]$ delivered
  and forwarded a message $\alpha_X$. Some \processes may have
  delivered messages about other partitions before or after
  $\alpha_X$.
  \begin{asparadesc}
  \item [\processes with last $\alpha_X$:] \Processes such as $a$
    where the last and best partition is still $P_X$. By propagating
    from \process to \process the corresponding $\delta_X$ message,
    these \processes purge $\alpha_X$.
  \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
    $\alpha_Y^y$, for $\alpha_Y^y< \alpha_X^x$:] \Processes such as
    \Process~$b$ that do not directly suffer from the non-delivery of
    $\delta_X$. They need to purge their own $P_Y$ if need
    be. Nonetheless, they deliver and forward $\alpha_Y$ that at least
    one following \process will receive.
  \item [\processes with $\delta_Y \rightarrow \alpha_X$:] \Processes
    such as \Process~$c$ that do not belong to the preceding category,
    for they already delivered $\delta_Y$. Nevertheless, best eventual
    forwarding guarantees that they receive $\alpha_Y$, which
    contradicts their history or state. In such a case, the detecting
    \processes purge their own $\alpha_X$. The detecting \processes
    must also notify subsequent \processes that their current
    partition \emph{may be} deleted. Indeed their parent may have
    blocked the corresponding $\delta$ messages and subsequent
    \processes must purge their possibly stale state, for the sake of
    consistency.  We note such a notification $\Delta_X$ to emphasize
    their proximity to $\delta_X$ messages.
    % the uncertainty of a $\delta$ message.
  \item [\processes with last $\alpha_X$ receiving $\Delta_X$ from
    their parent:] \Processes such as \Process~$d$ that have
    $\alpha_X$ but preceding delivered messages are not
    important. Such \processes must trust detecting \processes by
    delivering and forwarding $\Delta_X$. It is worth noting that
    these messages are subject to all aforementioned blocking
    conditions, but are also solved by aforementioned mechanisms.
  \end{asparadesc}

  Propagation~I terminates: a \process does not deliver a $\delta$
  message if it has already delivered it. Propagation~III terminates: a
  \process does not deliver a looping message.
  % ; and since \processes forward the messages they deliver, upstream
  % \processes eventually receive and may deliver messages detected as
  % issue. In Figure~\ref{fig:proofB}, \Process~$e$ eventually
  % receives $\delta_f$ from \Process~$b'$.
  These three phases propagation-detection-propagation ensure that
  \processes eventually purge stale $\alpha$ messages from the system,
  leaving room for best eventual forwarding of up-to-date messages.
  %
  %  \TODO{cannot loop add from $e$ , undo from $b'$ because $b'$ sent
  % delete to $e$, it will solve the inconsistency.}
  %
  %% In the meantime, \processes that still belong to a partition can
  %% propagate their respective last $\alpha$ message, and reach
  %% consistent partitioning.
\end{proof}

>>>>

\begin{proof}
  We must prove that every \process that delivered a stale $\alpha_X$
  eventually
  \begin{inparaenum}[(i)]
  \item delivers a better $\alpha_Y$, or 
  \item delivers a removal notification of $\alpha_X$.
  \end{inparaenum}
  Figure~\ref{fig:proofB} summarizes the issue of purging in scenarios
  involving concurrent operations:

  If every \process (such as $a$) starting from the source delivers
  and forwards a removal notification $\delta_X$ when their last
  delivery is $\alpha_X$, then every such \process eventually delivers
  the removal notification $\delta_X$ except \processes (such as $b$)
  that delivered $\alpha_X$ from a \process that delivered a message
  from another partition $\alpha_Y$ since then.

  These exceptions eventually receive and deliver $\alpha_Y$ since
  $\alpha_Y$ is better than $\alpha_X$ through this path, except if
  they already received and deliver the removal notification of $P_Y$
  (such as $c$). These \processes may never receive hence deliver
  $\delta_X$, and may never receive hence deliver a better message
  than $\alpha_X$. They need an additional mechanism to eventually
  purge $\alpha_X$ that cannot rely on the eventual purging of $P_Y$
  to avoid deadlocks.

  Assuming that every \process keeps an history of its past
  deliveries, \processes (such as $c$) can detect the inconsistency,
  since they receive from their parent an already deleted partition
  $P_Y$. This notification means that the parent discards any
  $\delta_Z$ with $\alpha_Z^z < \alpha_Y^y$, and most importantly, if
  $\delta_X$ exists, it discards it. To ensure the purge of stale
  messages, a detecting \process must assume the worst case that such
  $\delta_X$ exists, and send another kind of message, noted $\Delta$
  that notify the possible removal of $P_X$. Children \processes that
  still have $P_X$ as last delivery must trust the detecting \process
  and remove the possibly stale control information about $P_X$.

  %% Some \processes may have delivered messages about other partitions
  %% before or after $\alpha_X$. \Processes such as $b$ and $c$ delivered
  %% messages about $P_Y$.  For \processes such as $b$, the last delivery
  %% is $\alpha_Y$: $d_b(\_) \rightarrow \ldots \rightarrow d_b(\alpha_X)
  %% \rightarrow \ldots \rightarrow d_b(\alpha_Y)$; For \processes such
  %% as $c$, the last delivery is $\alpha_X$, and they delivered the
  %% addition and removal of $P_Y$: $d_c(\_) \rightarrow \ldots
  %% \rightarrow d_c(\alpha_Y) \rightarrow \ldots \rightarrow
  %% d_c(\delta_Y) \rightarrow \ldots \rightarrow d_c(\alpha_X)$. Both
  %% $a$ and $d$ delivered $\alpha_X$ last: $d_a(\_) \rightarrow \ldots
  %% \rightarrow d_a(\alpha_X)$. Their difference being their position in
  %% the chain: $d$ is a child of \processes that delivered messages
  %% about $P_Y$.

  %% \begin{asparadesc}
  %% \item [($a$ or $c$ or $d$) to ($a$ or $c$ or $d$):] The source is
  %%   like $a$.  By propagating from \process to \process the
  %%   corresponding $\delta_X$ message, these \processes purge
  %%   $\alpha_X$.
  %% \item [$a$ to $b$:] $b$ stops the propagation of $\delta_X$, for the
  %%   latter does not target its current partition.
  %% \item [$b$:] They need to purge their own $P_Y$, we must \TODO{prove
  %%   that $[a, b, c, d]$ is solved and that it does not require to
  %%   purge $P_Y$.}
  %% \item [$b$ to $d$:] would deliver $d_(\alpha_y)$ hence becoming $b$.
  %% \item [$b$ to $c$:] block $d_c(\alpha_y)$, so $c$ stays in $c$. But
  %%   it detects $b$ is its parent, and possibly blocked any delta with
  %%   its value $r_b(\delta_z) \rightarrow d_b(\delta_z)$. Since not
  %%   sure, $\Delta$

  %% \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
  %%   $\alpha_Y^y$, for $\alpha_Y^y< \alpha_X^x$:] \Processes such as
  %%   \Process~$b$ that do not directly suffer from the non-delivery of
  %%   $\delta_X$. They need to purge their own $P_Y$ if need
  %%   be. Nonetheless, they deliver and forward $\alpha_Y$ that at least
  %%   one following \process will receive.
  %% \item [\processes with $\delta_Y \rightarrow \alpha_X$:] \Processes
  %%   such as \Process~$c$ that do not belong to the preceding category,
  %%   for they already delivered $\delta_Y$. Nevertheless, best eventual
  %%   forwarding guarantees that they receive $\alpha_Y$, which
  %%   contradicts their history or state. In such a case, the detecting
  %%   \processes purge their own $\alpha_X$. The detecting \processes
  %%   must also notify subsequent \processes that their current
  %%   partition \emph{may be} deleted. Indeed their parent may have
  %%   blocked the corresponding $\delta$ messages and subsequent
  %%   \processes must purge their possibly stale state, for the sake of
  %%   consistency.  We note such a notification $\Delta_X$ to emphasize
  %%   their proximity to $\delta_X$ messages.
  %%   % the uncertainty of a $\delta$ message.
  %% \item [\processes with last $\alpha_X$ receiving $\Delta_X$ from
  %%   their parent:] \Processes such as \Process~$d$ that have
  %%   $\alpha_X$ but preceding delivered messages are not
  %%   important. Such \processes must trust detecting \processes by
  %%   delivering and forwarding $\Delta_X$. It is worth noting that
  %%   these messages are subject to all aforementioned blocking
  %%   conditions, but are also solved by aforementioned mechanisms.
  %% \end{asparadesc}

  %% Propagation~I terminates: a \process does not deliver a $\delta$
  %% message if it has already delivered it. Propagation~III terminates: a
  %% \process does not deliver a looping message.

  % ; and since \processes forward the messages they deliver, upstream
  % \processes eventually receive and may deliver messages detected as
  % issue. In Figure~\ref{fig:proofB}, \Process~$e$ eventually
  % receives $\delta_f$ from \Process~$b'$.
  These three phases propagation-detection-propagation ensure that
  \processes eventually purge stale $\alpha$ messages from the system,
  leaving room for best eventual forwarding of up-to-date messages.
  %
  %  \TODO{cannot loop add from $e$ , undo from $b'$ because $b'$ sent
  % delete to $e$, it will solve the inconsistency.}
  %
  %% In the meantime, \processes that still belong to a partition can
  %% propagate their respective last $\alpha$ message, and reach
  %% consistent partitioning.
\end{proof}
